\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-06-27 manuscript/paper.tex

Our model is clearly of JLCMs type, and can be viewed as a generalization of SREMs type in a much more flexible way. Table~\ref{table:shared_associations} gives common parameterizations for shared associations in SREMs. It is now common to include several of these in the survival sub-model, see for instance~\citet{}, but as far as we know, there is no method to consider simultaneously a huge number of associations and let the model learn which one is predictive for the underlying task it is trained for.

TODO : add REF :

Andrinopoulou, E.-R. and Rizopoulos, D. (2016). Bayesian shrinkage approach for a joint model of
longitudinal and survival outcomes assuming different association structures. Statistics in Medicine,
35(26):4813–4823.

Ferrer, L., Rondeau, V., Dignam, J., Pickles, T., Jacqmin-Gadda, H., \& Proust-Lima, C. (2016). Joint modelling of longitudinal and multi-state processes: application to clinical progressions in prostate cancer. Statistics in medicine, 35(22), 3933–3948. https://doi.org/10.1002/sim.6972

\begin{table}[htb]
\centering
\begin{tabular}{cccc}
\toprule
Description & $\Psi_a^l(t, \beta_k^l, b^l)$  & Reference \\
\midrule
Linear predictor & $m_k^l(t)$ & \citet{chi2006joint} \\ [.15cm]
Random effects & $b^l$  & \citet{hatfield2011joint} \\
Time-dependent slope & $\dfrac{\dd}{\dd t} m_k^l(t)$ & \citet{rizopoulos2011bayesian} \\ [.3cm]
Cumulative effect & $\int_0^t m_k^l(s) \dd s$ & \citet{andrinopoulou2017combined} \\ [.1cm]
 \bottomrule
\end{tabular}
\caption[]{Examples of classical shared associations in SREMs.}
\label{table:shared_associations}
\end{table}

>>>>

Our model is clearly of JLCMs type, and can be viewed as a generalization of SREMs type in a much more flexible way. Table~\ref{table:shared_associations} gives common parameterizations for shared associations in SREMs. It is now common to include several of these in the survival sub-model, see for instance~\citet{andrinopoulou2016bayesian, ferrer2016joint}, but as far as we know, there is no method to consider simultaneously a huge number of associations and let the model learn which one is predictive for the underlying task it is trained for.
\begin{table}[htb]
\centering
\begin{tabular}{cccc}
\toprule
Description & $\Psi_a^l(t, \beta_k^l, b^l)$  & Reference \\
\midrule
Linear predictor & $m_k^l(t)$ & \citet{chi2006joint} \\ [.15cm]
Random effects & $b^l$  & \citet{hatfield2011joint} \\
Time-dependent slope & $\dfrac{\dd}{\dd t} m_k^l(t)$ & \citet{rizopoulos2011bayesian} \\ [.3cm]
Cumulative effect & $\int_0^t m_k^l(s) \dd s$ & \citet{andrinopoulou2017combined} \\ [.1cm]
 \bottomrule
\end{tabular}
\caption[]{Examples of classical shared associations in SREMs.}
\label{table:shared_associations}
\end{table}
